Computer Science House By-Laws

### 2017-10-02 bylaws.tex
Clarify membership meeting requirements
Allow ad-hoc directorship meetings to count towards both
the introductory evaluations process as well as the spring
evaluations process

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\bylaw{Operations of the Evaluations Directorship}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\bsubsection{The Evaluation Period}
The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
\bsubsection{The Introductory Project}
Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
\bsubsection{Introductory Executive Board}
An Introductory Executive Board is elected by the Introductory Members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
The Introductory Executive Board consists of three members:
\begin{itemize}
	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
	\item A Vice President, who assists the President in leadership and representation.
	\item A Treasurer, who manages the finances for the project.
\end{itemize}
Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
\bsubsubsection{The Project}
The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
All of the proceeds go to a charity chosen in advance by the participants.
The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
\bsubsubsection{Introductory Project Advisors}
The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
\bsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
\begin{itemize}
	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
	\begin{itemize}
		\item Non-Resident members who have passed a Membership Evaluation
		\item Alumni members (not including Non-Resident Executive Board members)
		\item Honorary members
		\item Advisory members
	\end{itemize}
	\item A description of each Executive Board position, including:
	\begin{itemize}
		\item The responsibilities of the position
		\item The name(s) of the position’s member(s)
		\item The position’s weekly meeting time
	\end{itemize}
	\item A list of seven (7) annual House social events
	\item A list of seven (7) major House technical achievements
\end{itemize}
\bsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Be an active participant in the Introductory Project
\item Attend at least one House directorship meeting for each week of the process
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}

@@

\bsection{Expectations of House Members}
Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
Members are also required to actively participate in a majority of House activities.
\\* \\*
The member must participate significantly in at least one major project during the academic year.
The member is required to submit a description for this major project to the Executive Board for approval.
As an option to this requirement, the member may instead assist on a large number of House activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by the Executive Board.

>>>>

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\bylaw{Operations of the Evaluations Directorship}
\bsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\bsubsection{The Evaluation Period}
The Process lasts between six (6) and ten (10) weeks, starting when the Evaluations Director initiates it.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process.
\bsubsection{The Introductory Project}
Introductory members are expected to demonstrate initiative and an ability to work well in a group environment through the Introductory Project.
\bsubsection{Introductory Executive Board}
An Introductory Executive Board is elected by the Introductory Members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.
The Introductory Executive Board consists of three members:
\begin{itemize}
	\item A President, who leads the project and acts as primary representative to House through weekly status reports at House Meeting.
	\item A Vice President, who assists the President in leadership and representation.
	\item A Treasurer, who manages the finances for the project.
\end{itemize}
Introductory Members also elect a Secretary to take notes, and any number of additional non-voting leaders may be elected to take on project-specific tasks.
\bsubsubsection{The Project}
The Project is an annual fundraising event that takes place in the first semester of the Introductory Process.
All of the proceeds go to a charity chosen in advance by the participants.
The Executive Board is encouraged to discuss the Project and following an open ballot Simple Majority Vote, may choose to intervene in the Introductory Project if the Project does not appear to fulfill requirements.
\bsubsubsection{Introductory Project Advisors}
The Evaluations Director may choose between one (1) and three (3) House members to be Introductory Project Advisors.
The advisors assist in organizing the participants at the beginning of the Introductory Project and thereafter act as a resource to keep the Project running smoothly.
\bsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain the following:
\begin{itemize}
	\item A signature from all Active/Introductory Resident members, each Executive Board member, and fifteen (15) of any combination of the following:
	\begin{itemize}
		\item Non-Resident members who have passed a Membership Evaluation
		\item Alumni members (not including Non-Resident Executive Board members)
		\item Honorary members
		\item Advisory members
	\end{itemize}
	\item A description of each Executive Board position, including:
	\begin{itemize}
		\item The responsibilities of the position
		\item The name(s) of the position’s member(s)
		\item The position’s weekly meeting time
	\end{itemize}
	\item A list of seven (7) annual House social events
	\item A list of seven (7) major House technical achievements
\end{itemize}
\bsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Be an active participant in the Introductory Project
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad-Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}

@@

\bsection{Expectations of House Members}
Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings).
Members are also required to actively participate in a majority of House activities.
\\* \\*
The member must participate significantly in at least one major project during the academic year.
The member is required to submit a description for this major project to the Executive Board for approval.
As an option to this requirement, the member may instead assist on a large number of House activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by the Executive Board.
